Viscous Erosion in Porous Media

### 2018-03-20 docs/methods/erosion_methods.tex
small changs to intro

\begin{abstract} 
We develop numerical methods to simulate the fluid-mechanical erosion of
many bodies (order 50) in a two-dimensional Stokes flow. The broad aim
is to simulate the erosion of a porous medium (e.g.~ground water flow)
with grain scale resolution. Our fluid solver is based on a
boundary integral formulation of the Stokes equations. We solve the
associated linear system with a fast-multipole-accelerated GMRES iteration. We use a second-kind integral equation so
that GMRES requires a bounded iteration count (independent of the number
of unknowns). To evolve the individual grains under shear-driven
erosion, we regularize via curvature-penalization and solve the
associated system using the {\thL} formulation. This framework allows
numerically stable treatment of stiff terms, thus permitting large time
steps. The overall accuracy of our method is exponential in space and
second-order in time. The method is computationally efficient, with the
fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration, and a one-time
$\mathcal{O}(N^2)$ computation to compute the shear stress. We benchmark single-body results against analytical predictions. In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact. The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
\end{abstract}

\begin{keyword}
  Stokes flow \sep Erosion \sep Boundary integral method \sep Shear
  stress \sep {\thL} formulation
\end{keyword}

@@

\newpage

Good word: Spontaneous channelization

\vsp{3}
Possible list:
\begin{itemize}
\item Show multiple body simulation with fixed flow rate
\item Then simulation with fixed pressure drop
\item GMRES counts
%
\item $\bigO(5-10)$ bodies
	\begin{itemize}
	\item Area and Drag
	\item Long channels between flat faces
	\end{itemize}
\item $\bigO(50)$ bodies
	\begin{itemize}
	\item Area and Drag
	\end{itemize}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
\section{Error estimates for near-singular integration \label{A:AppendixA}} 
\end{appendices}

>>>>

\begin{abstract} 
We develop numerical methods to simulate the fluid-mechanical erosion of
many bodies in a two-dimensional Stokes flow. The broad aim
is to simulate the erosion of a porous medium (e.g.~ground water flow)
with grain-scale resolution. Our fluid solver is based on a
second-kind boundary integral formulation of the Stokes equations that is
discretized with a spectrally-accurate Nystr\"om method and solved
with a fast-multipole-accelerated GMRES iteration. To evolve the individual grains under shear-driven
erosion, we regularize via curvature-penalization and solve the
associated system using the {\thL} formulation. This framework allows
numerically stable treatment of stiff terms, thus permitting large time
steps. The overall accuracy of our method is exponential in space and
second-order in time. The method is computationally efficient, with the
fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration,
a mesh-independent number of GMRES iterations, and a one-time
$\mathcal{O}(N^2)$ computation to compute the shear stress. We benchmark single-body results against analytical predictions. In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact. The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
\end{abstract}

\begin{keyword}
  Porous medium \sep Stokes flow \sep Erosion \sep Boundary integral
  equations \sep Shear stress \sep {\thL} formulation
\end{keyword}

@@

{\bf Good word: Spontaneous channelization}

@@

\todo[inline]{paper of Bryan, Eric, and Pieter and one with Pietro,
George, and Ruben}
